Concurrent Programming with Harmony

### 2020-08-30 book/paper.tex
Got rid of PushAddress

\begin{figure}
\begin{code}
\begin{verbatim}
code/Up.hny:1 def incrementer(self):
   0 Jump 25
   1 Frame incrementer self
code/Up.hny:2     count = count + 1;
   2 Load count
   3 Push 1
   4 2-ary +
   5 Store count
code/Up.hny:3     done[self] = True;
   6 PushAddress done
   7 LoadVar self
   8 Address
   9 Push True
   10 Store
   11 Return
code/Up.hny:5 def main():
   12 Jump 25
   13 Frame main ()
code/Up.hny:6     await all(done);
   14 Load done
   15 1-ary all
   16 JumpCond False 14
code/Up.hny:7     assert count == 2, count;
   17 AtomicInc
   18 Load count
   19 Push 2
   20 2-ary ==
   21 Load count
   22 Assert2
   23 AtomicDec
   24 Return
code/Up.hny:9 count = 0;
   25 Push 0
   26 Store count
code/Up.hny:10 done = [ False, False ];
   27 Push [False, False]
   28 Store done
code/Up.hny:11 spawn incrementer(0);
   29 Push 0
   30 Dup
   31 Push PC(1)
   32 Spawn
\end{verbatim}
\end{code}
\caption{The first part of the HVM bytecode corresponding to \autoref{fig:inc}.}
\label{fig:inccode}
\end{figure}

@@

{\small
\begin{tabular}{|l|l|}
\hline
Address & compute address from two components \\
\hline
Apply & pop $m$ and $i$ and apply $i$ to $m$, pushing a value \\
\hline
Assert & pop $b$ and check that it is \texttt{True} \\
\hline
AtomicInc & increment the atomic counter of this context \\
\hline
AtomicDec & decrement the atomic counter of this context \\
\hline
Continue & no-op (but causes a context switch) \\
\hline
Choose & choose an element from the set on top of the stack \\
\hline
Cut & pop set or dict and push minimum and remainder \\
\hline
Del [$v$] & delete shared variable $v$ \\
\hline
DelVar [$v$] & delete process variable $v$ \\
\hline
Dict & pop $n$ and $n$ key/value pairs and push a dictionary \\
\hline
Dup & duplicate the top element of the stack \\
\hline
Frame \texttt{m} $a$ & start method \texttt{m} with arguments $a$,
initializing variables.  \\
\hline
Go & pop context and value, push value on context's stack, and add to context bag \\
\hline
Jump $p$ & set program counter to $p$ \\
\hline
JumpCond $e$ $p$ & pop expression and, if equal to $e$, set program counter to $p$ \\
\hline
Load [$v$] & push the value of a shared variable onto the stack \\
\hline
LoadVar [$v$] & push the value of a process variable onto the stack \\
\hline
Move $i$ & move stack element at offset $i$ to top of the stack \\
\hline
$n$-ary \textit{op} & apply $n$-ary operator \textit{op} to the top $n$ elements on the stack \\
\hline
Pop & pop a value of the stack and discard it \\
\hline
Push $c$ & push constant $c$ onto the stack \\
\hline
PushAddress $v$ & push the address of variable $v$ \\
\hline
Return & pop return address, push \texttt{result}, and restore program counter \\
\hline
Set & pop $n$ and $n$ elements and push a set of the elements \\
\hline
SetIntLevel & pop $e$, set interrupt level to $e$, and push old interrupt level \\
\hline
Spawn & pop tag, argument, and method and spawn a new context \\
\hline
Split & pop tuple and push its elements \\
\hline
Stop [$v$] & save context into shared variable $v$ and remove from context bag \\
\hline
Store [$v$] & pop a value from the stack and store it in a shared variable \\
\hline
StoreVar [$v$] & pop a value from the stack and store it in a process variable \\
\hline
Trap & pop interrupt argument and method \\
\hline
\end{tabular}
}

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
code/Up.hny:1 def incrementer(self):
   0 Jump 25
   1 Frame incrementer self
code/Up.hny:2     count = count + 1;
   2 Load count
   3 Push 1
   4 2-ary +
   5 Store count
code/Up.hny:3     done[self] = True;
   6 Push ?done
   7 LoadVar self
   8 Address
   9 Push True
   10 Store
   11 Return
code/Up.hny:5 def main():
   12 Jump 25
   13 Frame main ()
code/Up.hny:6     await all(done);
   14 Load done
   15 1-ary all
   16 JumpCond False 14
code/Up.hny:7     assert count == 2, count;
   17 AtomicInc
   18 Load count
   19 Push 2
   20 2-ary ==
   21 Load count
   22 Assert2
   23 AtomicDec
   24 Return
code/Up.hny:9 count = 0;
   25 Push 0
   26 Store count
code/Up.hny:10 done = [ False, False ];
   27 Push [False, False]
   28 Store done
code/Up.hny:11 spawn incrementer(0);
   29 Push 0
   30 Dup
   31 Push PC(1)
   32 Spawn
\end{verbatim}
\end{code}
\caption{The first part of the HVM bytecode corresponding to \autoref{fig:inc}.}
\label{fig:inccode}
\end{figure}

@@

{\small
\begin{tabular}{|l|l|}
\hline
Address & compute address from two components \\
\hline
Apply & pop $m$ and $i$ and apply $i$ to $m$, pushing a value \\
\hline
Assert & pop $b$ and check that it is \texttt{True} \\
\hline
AtomicInc & increment the atomic counter of this context \\
\hline
AtomicDec & decrement the atomic counter of this context \\
\hline
Continue & no-op (but causes a context switch) \\
\hline
Choose & choose an element from the set on top of the stack \\
\hline
Cut & pop set or dict and push minimum and remainder \\
\hline
Del [$v$] & delete shared variable $v$ \\
\hline
DelVar [$v$] & delete process variable $v$ \\
\hline
Dict & pop $n$ and $n$ key/value pairs and push a dictionary \\
\hline
Dup & duplicate the top element of the stack \\
\hline
Frame \texttt{m} $a$ & start method \texttt{m} with arguments $a$,
initializing variables.  \\
\hline
Go & pop context and value, push value on context's stack, and add to context bag \\
\hline
Jump $p$ & set program counter to $p$ \\
\hline
JumpCond $e$ $p$ & pop expression and, if equal to $e$, set program counter to $p$ \\
\hline
Load [$v$] & push the value of a shared variable onto the stack \\
\hline
LoadVar [$v$] & push the value of a process variable onto the stack \\
\hline
Move $i$ & move stack element at offset $i$ to top of the stack \\
\hline
$n$-ary \textit{op} & apply $n$-ary operator \textit{op} to the top $n$ elements on the stack \\
\hline
Pop & pop a value of the stack and discard it \\
\hline
Push $c$ & push constant $c$ onto the stack \\
\hline
Return & pop return address, push \texttt{result}, and restore program counter \\
\hline
Set & pop $n$ and $n$ elements and push a set of the elements \\
\hline
SetIntLevel & pop $e$, set interrupt level to $e$, and push old interrupt level \\
\hline
Spawn & pop tag, argument, and method and spawn a new context \\
\hline
Split & pop tuple and push its elements \\
\hline
Stop [$v$] & save context into shared variable $v$ and remove from context bag \\
\hline
Store [$v$] & pop a value from the stack and store it in a shared variable \\
\hline
StoreVar [$v$] & pop a value from the stack and store it in a process variable \\
\hline
Trap & pop interrupt argument and method \\
\hline
\end{tabular}
}
